---
title: "Hobbies: Volunteering"
format: html
---

```{r setup, include=FALSE}
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# ðŸŒ± My Volunteering Journey

In my free time, I find joy and purpose in volunteering. It started as a way to give back to my community, but it has become a meaningful part of my life that teaches me about empathy, teamwork, and gratitude.

## ðŸ“… Where I Volunteer

### **1. Community Food Bank (Every end of the month)**
Every last weekend of the month from 9 AM to 12 PM, I help at Hougang SunLove Centre where I:
- Sort and pack food donations
- Assist with distribution to families in need
- Help organize inventory

### **2. KidsLearn**
I volunteered as a phonics tutor for kindergarten students every Saturday morning under Youth Corps:
- Prepare simple, engaging phonic activities in the Khan Academy Kids app
- See students gain confidence in their abilities
- Build rapport with kids from diverse backgrounds

### **3. Special Events**
Occasionally, I help with:
- Charity runs and fundraising events
- Holiday donation drives
- Community festivals

## ðŸ’¡ Why I Volunteer

```{r volunteering-hours, fig.height=5}
# Simple visualization of volunteering hours - SIMPLIFIED VERSION
volunteer_data <- data.frame(
  Activity = c("Food Bank", "Tutoring", "Special Events"),
  Hours = c(120, 80, 30)
)

# Order the activities by hours
volunteer_data$Activity <- factor(volunteer_data$Activity,
                                  levels = volunteer_data$Activity[order(volunteer_data$Hours)])

ggplot(volunteer_data, aes(x = Activity, y = Hours, fill = Activity)) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_text(aes(label = paste(Hours, "hrs")), 
            hjust = -0.2, 
            size = 5, 
            fontface = "bold") +
  scale_fill_manual(values = c("#2E86AB", "#A23B72", "#C73E1D")) +
  labs(title = "My Volunteering Hours (Past Year)",
       x = "",
       y = "Hours") +
  coord_flip() +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold")
  ) +
  ylim(0, 130)  # Set y-axis limit slightly above max value
```

## ðŸ¤ How to Get Involved

If you're interested in volunteering:

1. **Start small** - Even 2 hours a month makes a difference
2. **Choose what you enjoy** - You'll stick with it longer
3. **Check local websites** for volunteer opportunities
4. **Bring a friend** - It's more fun together!

## ðŸŒŸ What Volunteering Has Taught Me

- **Gratitude:** Appreciating what I have
- **Patience:** Things take time to improve
- **Community:** We're all connected
- **Leadership:** Taking initiative in group activities
- **Balance:** Making time for both studies and service

---

*"The best way to find yourself is to lose yourself in the service of others."* - Mahatma Gandhi

**Volunteering has taught me that small actions, when multiplied by many people, can transform the world.**

[â† Back to Home](index.qmd) | [View My Projects â†’](data-visualization.qmd)